KIN: A method to infer relatedness from low-coverage ancient DNA

### 2022-05-16 paper_overleaf/main.tex
Updates from Overleaf

Only for 28 pairs, KIN has confident classifications that differ from those obtained using READ (table S2, figure S11). For 20 of these comparisons, KIN predicts a third-degree relationship, which READ classifies as unrelated.

lcMLkin predicts $3^{rd}$ - $5^th$ in 14 of these cases, unrelated in 1 case, second degree in 1 case, and does not have enough data for classification in 4 cases. Since READ does not infer third degree, and lcMLkin infers a group of relatedness together as $3^{rd}$ - $5^th$, it is likely that KIN is able to correctly resolve these cases. For 10 additional pairs, lcMLkin predicts $3^{rd}$ - $5^th$ degree, but KIN infers them to be unrelated. Thus, these are likely examples of $4^{th}$ or $5^{th}$ degree relations.

For less than third-degree relations, only eight cases are classified differently between KIN and READ. lcMLkin matches KIN's prediction in two cases, and does not have enough data in 5 cases. In the last case, all three methods differ (table S3). Finally, there are three disagreements between KIN and lcMLkin in classification of parent-child versus siblings (READ predicts first degree for all three pairs). We plotted the pairwise differences for these three pairs in Fig. S12, and found that the proportion of differences along the genome aligns with the prediction of KIN.

>>>>

Only for 28 pairs, KIN has confident classifications that differ from those obtained using READ (table S2, Fig. S11). For 20 of these comparisons, KIN predicts a third-degree relationship, which READ classifies as unrelated.

lcMLkin predicts $3^{rd}$ - $5^th$ in 14 of these cases, unrelated in 1 case (see Fig. S11), second degree in 1 case (see Fig. S11), and does not have enough data for classification in 4 cases. Since READ does not infer third degree, and lcMLkin infers a group of relatedness together as $3^{rd}$ - $5^th$, it is likely that KIN is able to correctly resolve these cases. For 10 additional pairs, lcMLkin predicts $3^{rd}$ - $5^th$ degree, but KIN infers them to be unrelated. Thus, these are likely examples of $4^{th}$ or $5^{th}$ degree relations.

For less than third-degree relations, only eight cases are classified differently between KIN and READ. lcMLkin matches KIN's prediction in two cases, and does not have enough data in 5 cases. In the last case, all three methods differ (table S3, Fig. S11). Finally, there are three disagreements between KIN and lcMLkin in classification of parent-child versus siblings (READ predicts first degree for all three pairs). We plotted the pairwise differences for these three pairs in Fig. S12, and found that the proportion of differences along the genome aligns with the prediction of KIN.
